Analysis of pleiotropy of eQTLs

### 2023-01-18 presentation_230120_internal_seminar/intern_sem_230120.tex
DOC

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}
        \frametitle{Genome-wide association studies (GWAS)}

        \begin{itemize}
            \item Genetic alleles with higher frequency in individuals with a given disease
            \item A very active field with many studies
            \item Many genetic variants are involved in several phenotypes
        \end{itemize}
%
        \vfill
%
        Questions:
%
        \begin{itemize}
            \item Correlation between variants. Which is the causal variant?
            \item Which cell type important for disease?
            \item Over 90\% GWAS variants are non-coding. What is their role?
        \end{itemize}
%
        \vfill
%
        Questions partially addressed by looking at eQTLs in different tissues

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    The associations to diseases are heterougeneously distributed in the genome, Watanabe & Posthuma
%    This is based on loci associated to multiple traits
    \begin{frame}
        \frametitle{Genome-wide association studies (GWAS)}

        \begin{itemize}
            \item Association test of effect allele on case individuals
            \item High-throughput genetics: 3000 unique loci for over 250 disease/trait outcomes\footnote{Loos 2020. 10.1038/s41467-020-19653-5}
            \item Of the 1,707.0 Mb genome, 90.0\% is associated to different GWAS categories
        \end{itemize}
%
        \vfill
%          However, how do we know if these variants are active in a tissue,
%         or whether these variants false positives due to linkage disequilibrium,
%         or how these variants act molecularly
        Questions:
%
        \begin{itemize}
            \item Correlation between variants. Which is the causal variant?
            \item Which cell types important for disease?
            \item In which tissues are these variants active?
        \end{itemize}
%
        \vfill
%
        Questions partially addressed by looking at eQTLs in different tissues

        \blfootnote{}
        \blfootnote{Cano-Gamez et al. 2020. doi:10.3389/fgene.2020.00424}
    \end{frame}
